\begingroup 
\anonsection{Источники и литература}
\begin{thebibliography}{00}

\bibitem{aphyr}
	Kingsbury K., Strong consistency models
	[Электронный ресурс] //
	Aphyr
	URL: https://aphyr.com/posts/313-strong-consistency-models
	(дата обращения: 17.04.2016)
	
\bibitem{brewer}
	Brewer E., Towards Robust Towards Robust Distributed Systems
	[Электронный ресурс] //
	PODC Keynote
	URL: http://people.eecs.berkeley.edu/~brewer/cs262b-2004/PODC-keynote.pdf
	(дата обращения: 11.03.2016)
	
\bibitem{cap-proof}
	Gilbert S., Lynch N., Brewer’s Conjecture and the Feasibility of Consistent, Available, Partition-Tolerant Web Services //
	ACM SIGACT News. -- 2002. -- Volume 33 Issue 2, June 2002. -- cс. 51-59
	
\bibitem{luhn}
	Luhn H. P., A Statistical Approach to Mechanized Encoding and Searching of Literary Information //
	IBM Journal of Research and Development. -- 1957. -- Volume 1 Issue 4, October 1957. -- cс. 309-317
	
\bibitem{jones}
	Jones K. S., A statistical interpretation of term specificity and its application in retrieval //
	Document retrieval systems. -- 1988. -- cc. 132-142
	
\bibitem{google}
	Brin S., Page L., The anatomy of a large-scale hypertextual Web search engine //
	WWW7 Proceedings of the seventh international conference on World Wide Web 7. -- 1998 -- сс. 107-117

\bibitem{lucene}
	Białecki A., Muir R., Ingersoll G., Apache Lucene 4 \\
	SIGIR 2012 Workshop on Open Source Information Retrieval
	URL: http://opensearchlab.otago.ac.nz/paper\_10.pdf
	(дата обращения: 22.05.2016)
	
\bibitem{lina}
	McCandless M., Hatcher E., Gospodnetić O., Lucene in Action,
	2-e изд. -- Manning, 2010 -- 488 с.
	
\bibitem{eina}
	Gheorghe R., Matthew Hinman L., Russo R., Elasticsearch in Action, -- Manning, 2015 -- 496 с.

\bibitem{solr-vs-es-features}
	Apache Solr vs Elasticsearch
	[Электронный ресурс] //
	Kelvin Tan
	URL: http://solr-vs-elasticsearch.com/
	(дата обращения: 23.05.2016)
	
\bibitem{solr-vs-es-perf-1}
	Elasticsearch vs. Solr performance: round 2
	[Электронный ресурс] //
	flax
	URL: http://www.flax.co.uk/blog/2015/12/02/elasticsearch-vs-solr-performance-round-2/
	(дата обращения: 23.05.2016)
	
\bibitem{solr-vs-es-perf-2}
	Realtime Search: Solr vs Elasticsearch
	[Электронный ресурс] //
	Socialcast
	URL: http://blog.socialcast.com/realtime-search-solr-vs-elasticsearch/
	(дата обращения: 23.05.2016)

\end{thebibliography}
\endgroup

\clearpage
